Estimating demographic bias on tests of children's early vocabulary

### 2022-02-01 paper/cogsci.tex

\begin{abstract}
Children's early language skill has been linked to later educational
outcomes, making it important to measure early language accurately.
Parent-reported instruments such as the Communicative Development
Inventories (CDIs) have been shown to provide reliable and valid
measures of children's aggregate early language skill. However, CDIs
contain hundreds of vocabulary items, some of which may not be heard
(and thus learned) equally often by children of varying backgrounds.
This study used a database of American English CDIs to identify words
that showed strong bias for particular demographic groups of children,
on dimensions of sex (male vs.~female), race (white vs.~non-white), and
maternal education (high vs.~low). For each dimension, we identified
dozens of strongly biased items, and showed that eliminating these items
reduced the expected ability difference between groups. Additionally, we
investigated how well the relative frequency of words spoken to young
girls vs.~boys predicted sex-based word learning bias, and discuss
possible sources of demographic differences in early word learning.

\textbf{Keywords:}
language acquisition; word learning; measuring instrument bias;
demographics;
\end{abstract}

@@

We analyze parent-reported Wordbank data from 5520 American English CDI:
Words \& Sentences administrations for children 16 to 30 months of age
(Frank, Braginsky, Yurovsky, \& Marchman, 2017, 2021). Full demographic
data are not reported in some datasets contributed to Wordbank: sex was
available for 4094 children, race/ethnicity was available for 2715
children, and maternal education (a proxy for socioeconomic status; SES)
was available for 5520 children.

The analysis of sex-based differences included CDI administrations from
1989 female and 2105 male children. The analysis of race-based
differences included data from 2202 white, 67 Asian, 222 Black, 131
Hispanic, and 93 ``Other'' children. Due to sparse data for many
categories, we binarized participants' race/ethnicity as White (2202) or
Non-white (513), recognizing that there may be important variation
between groups that this will fail to capture. Data for the maternal
education analysis included CDI data from children whose mother's had
the following levels of education: 8 with no more than primary school
education, 123 with some secondary school, 416 with no more than
secondary school, 613 with some college, 870 with no more than a college
degree, 162 with no more than some graduate school, and 584 with a
graduate degree. Again due to data sparsity, we binarized the 4973
children whose mothers had at least some college or more as high
maternal education (high-ME), and those whose mothers had at most high
school (547 children) as low maternal education (low-ME).

@@

First, we will examine the size of demographic effects on language
ability in a baseline Rasch model fitted without regard to demographic
group. Then we will fit a multigroup Rasch model for each demographic
factor, and characterize the between-group differences in item
difficulties. Next, we will re-examine the size of demographic effects
after pruning biased items from the CDI:WS using a varying threshold.
Finally, we measure the strength of association between sex-related
differences in language input and the degree of sex-related DIF.

\hypertarget{demographic-effects-in-baseline-rasch-model}{%
\subsection{Demographic effects in baseline Rasch
model}\label{demographic-effects-in-baseline-rasch-model}}

@@

Figure 2 shows GLIMMERs for a selection of CDI items for sex (left),
maternal education (middle), and race (right). The full GLIMMERs, with
all 680 CDI:WS items, are available on
\href{https://osf.io/57rsw/?view_only=2b6ecb61fe08458293af7421d276932a}{OSF},
but were too large to include here. It is important, however, to inspect
the full plots, for if there is a cluster of items in a GLIMMER, the
analyst may conclude that these items are strong candidates for DIF on
that dimension. For example, there is some clustering at the top and
bottom of Figure 2: at the top, ``vagina''\footnote{Parents using the
  CDI are instructed to check genital items if the child produces
  whatever word the family uses.}, ``tights,'' ``dress (object),'' and
``doll'' form a cluster of items that are much more well-known for
females, while at the bottom, ``penis'' stands out as much more
well-known by males. For the maternal education and race GLIMMERs
(Figures 3 and 4)--and in the rest of the full sex GLIMMER, there are
not clusters, but rather a continuum of smoothly varying differences
with overlap. This makes identifying items with DIF quite difficult, as
different methods are likely to yield inconsistent results (Stenhaug,
Frank, \& Domingue, 2021). Hence, we next characterized the
distributions of the item-level group difficulty differences, and
measured the influence of pruning a varying number of items on the
demographic effect sizes.

@@

For sex, the median difficulty difference (male-female) was 0.28
(M=0.27, sd=0.4), with 593/680 items being easier for females than
males. The fact that the bulk of this distribution favors females shows
that the female language advantage is pervasive across the CDI:WS, and
suggests that it is likely to be a real ability advantage, unless the
bulk of these items are actually spoken more often to female children
than to male children.

@@

For maternal education (ME), the median difficulty difference (low-high)
was -0.01 (M=0.03, sd=0.55), with 337/680 items being easier for high-ME
than low-ME children. With the mean and median difficulty differences
close to 0, and roughly half of the words favoring each ME group, it is
tempting to conclude that the CDI:WS items are somewhat balanced with
respect to ME (and thus SES, by proxy).

@@

Given the smoothly-varying distributions of DIF shown by each
demographic factor, we chose to evaluate multiple thresholds for pruning
the extreme-valued items from each distribution. For each demographic
factor, we pruned items with difficulty difference from the mean at
varying thresholds, from \textgreater.25 SD to \textgreater3 SD, in
increments of .25 SD. At each SD threshold, a potentially different
subset of items are excluded for each model, but with the goal of
creating a single CDI that is less biased on all dimensions, we pruned
the union of the subsets excluded from each model. For example, pruning
\textgreater2SD from the mean of each model excluded 25 sex-biased
items, 39 ME-biased items, and 31 race-biased items, with their union
being 76 unique items. Figure 3 shows the demographic effects
(\(\beta\)s) at different exclusion thresholds.

@@

Where is the exclusion threshold that jointly minimizes the effect sizes
of these demographic variables? The strict exclusion of all items with
\textgreater.25 SD difficulty difference -- 661/680 (97\%) of the CDI:WS
-- best optimized this, but seems too extreme of a culling. The next
best thresholds are \textgreater.5 SD -- again, too extreme -- or 3 SD,
a remarkably lax criterion that only excludes 19 items in total (11 due
to sex bias). Only slightly worse than these is \textgreater2.25 SD,
which excludes 59 items (9\% of the CDI:WS), and shows a modest effect
of both race (\(\beta=0.48\)) and maternal education (\(\beta=.19\)),
and a near-median effect size for sex (\(\beta=-.59\)). We characterize
these 59 potentially biased items below, and consider whether we might
recommend pruning them from the CDI:WS.

@@

Demographic differences in language ability are likely to be at least
partially explained by differences in linguistic input received by
children in different groups. Indeed, input quantity (total daily
tokens) and some measures of quality (e.g., lexical diversity: ratio of
word types vs.~tokens) have often been predictive of language learning
outcomes in demographic studies (Huttenlocher, Haight, Bryk, Seltzer, \&
Lyons, 1991; Rowe \& Goldin-Meadow, 2009). We used a corpus-based
analysis to investigate the extent to which word frequency in
child-directed speech to male vs.~female children was predictive of the
amount of sex-based bias shown by CDI items. Similar to the approach
taken by Braginsky, Meylan, \& Frank (2016), we used the CHILDES corpus
of transcripts from dyadic play sessions (MacWhinney, 2000), which are
labeled with the sex of the target child, but not other demographic
variables. We found a total of 5213750 female-directed tokens and
6091950 male-directed tokens that matched 662 of the 680 CDI:WS items,
normalized the word frequencies to tokens per million for each target
sex, and calculated the log-odds of each word being spoken to a female
(i.e., \(log(p_{f} / p_{m}\)), meaning unbiased words will have log-odds
of 0, while those spoken more often to females will have log-odds
\(>0\), and those spoken more often males will have log-odds \(<0\). For
example ``doll'' was spoken 156 times to females, and 138 times to
males, thus \(p_{f} = 156/(156+138) = .53\), \(p_{m} = 1-p_{f} = 0.47\),
and \(log(p_{f}/p_{m})\) = 0.12), while ``police'' was spoken 138 times
to females, and 225 times to males, and thus has log-odds = -0.49).
Overall, the correlation between the log-odds of a word being spoken to
a female vs.~a male child and the size of the female (vs.~male)
advantage for that CDI word was modest, but significant (\(r=0.18\),
\(p<.001\)), suggesting that some of the sex bias seen in CDI items is
explained by differences in language input received by girls vs.~boys.

@@

We investigated the CDI:WS, a popular parent-report measure of
children's early vocabulary, for potential demographic bias, examining
the distribution of words' estimated difficulties for children of
mothers with high- vs.~low-education children (a proxy for family SES),
females vs.~males, and for white vs.~non-white children. The IRT-based
analysis revealed differential item functioning (DIF) for many items
along each demographic dimension, but only in the case of sex were clear
clusters of items that were more well-known to females (including
feminine clothing and genitalia), and a clear item that was more
well-known to males (male genitalia). For the rest of the items, and for
SES- and race-based analysis, there was a smooth continuum of DIF,
making the boundary of true DIF subjective, as this would rely on
knowing the true difference in language ability between groups--which we
reciprocally estimate from instruments like the CDI. To move forward, we
identified candidate DIF items systematically pruning the extremes of
each distribution, excluding outliers for each demographic across a
range of thresholds, and seeking to minimize the size of demographic
effects. Although many exclusion thresholds decreased the size of
maternal education and race effects, the female advantage actually grew
under most prunings, with the majority of excluded extrema being
stereotypically-male nouns (e.g, ``truck,'' ``fireman'').

This analysis highlights a fundamental difficulty of identifying DIF: an
analyst must either know the expected magnitude of an ability difference
between the two demographic groups, or know a set of ``anchor'' items
that are equally difficult (i.e., unbiased) for both groups (for an
overview, see Stenhaug, Frank, \& Domingue, 2021). But in the universe
of children's early language, there is only a finite set of
early-learned words to choose from--and we may expect many of them to be
biased for various environmental reasons (e.g., boys and girls know
their respective genitalia; children in Florida may not use mittens or
skis). Hence, the presence of DIF on a set of items could indicate a
degree of varying linguistic input, rather than an actual advantage for
one demographic over another.

Choosing an exclusion threshold that struck a balance of reducing race-
and ME-based bias and not eliminating too many items, we identified 59
suspect items--the majority of which favored white/high-ME groups. These
extrema were predominantly nouns, including many animals (esp.~for
maternal education), vehicles and professions (esp.~for sex). Notably,
no verbs and few syntactically complex items were identified as
outliers, which may suggest that these lexical classes are less prone to
environmental influence, and perhaps more generally unbiased. Pruning
these 59 outliers would decrease the demographic effects of maternal
education (unpruned \(\beta=.23\); pruned \(\beta=.19\)) and race
(unpruned \(\beta=.50\); pruned \(\beta=.48\)). In contrast, the
majority of the sex-biased outliers were easier for the disadvantaged
group (males), meaning that the removal of these extrema increased the
female language advantage on the CDI:WS (unpruned \(\beta=0.56\); pruned
\(\beta=.59\)). In aggregate, these analyses seem to suggest that the
CDI:WS may slightly overestimate the magnitude of differences in
language ability along the dimensions of maternal education and race,
and perhaps underestimate the female advantage.

This investigation is only a first step in measuring demographic bias in
the items on the CDI:WS. More research is needed to determine which CDI
items that show DIF are more subject to environmental influence, as we
found only a modest association between the relative frequency of words
in child-directed speech to boys vs.~girls and the amount of sex-based
DIF. Examining the relative frequency of CDI words across households
with varying maternal education and race may reveal similarly weak
associations, or there may be strong associations only among particular
categories of words. It may be that particular activity
contexts--popular with some demographic groups, and not others--may be
predictive. For example, many of the extrema favoring high-ME children
are animals and animal sounds (e.g., ``quack quack,'' ``woof woof,''
``baa baa,'' ``duck,'' ``sheep,'' ``giraffe,'' ``zebra''): do high-SES
households visit the zoo more often, or perhaps engage in other
activities related to naming animals and noises they make (e.g., animal
noise toys)? If certain activities are driving early word learning for
high-ME children, what are the activities (and associated vocabulary)
that low-SES households are instead engaging in? Note, too, that SES,
race, and sex are only three of many possible demographic dimensions of
interest. For example, geographic region is likely predictive of
children's early experience with (and thus knowledge of) CDI items
related to winter weather (e.g., ``snow,'' ``mittens'') or outdoors
activities (e.g.~``camping''). A truly fair test of children's early
vocabulary would contain a representative and balanced sample of words
from all activities that children engage in, across demographic groups.

>>>>

\begin{abstract}
Children's early language skill has been linked to later educational
outcomes, making it important to measure early language accurately.
Parent-reported instruments such as the Communicative Development
Inventories (CDIs) have been shown to provide reliable and valid
measures of children's aggregate early language skill. However, CDIs
contain hundreds of vocabulary items, some of which may not be heard
(and thus learned) equally often by children of varying backgrounds.
This study used a database of American English CDIs to identify words
demonstrating strong bias for particular demographic groups of children,
on dimensions of sex (male vs.~female), race (white vs.~non-white), and
maternal education (high vs.~low). For each dimension, we identified
dozens of strongly biased items, and showed that eliminating these items
reduced the expected ability difference between groups. Additionally, we
investigated how well the relative frequency of words spoken to young
girls vs.~boys predicted sex-based word learning bias, and discuss
possible sources of demographic differences in early word learning.

\textbf{Keywords:}
language acquisition; word learning; measuring instrument bias;
demographic bias
\end{abstract}

@@

We analyzed parent-reported Wordbank data from 5520 American English
CDI: Words \& Sentences administrations for children 16 to 30 months of
age (Frank, Braginsky, Yurovsky, \& Marchman, 2017, 2021). Full
demographic data are not reported in some datasets contributed to
Wordbank: sex was available for 4094 children, race/ethnicity was
available for 2715 children, and maternal education (a proxy for
socioeconomic status; SES) was available for 5520 children.

The analysis of sex-based differences included CDI administrations from
1989 female and 2105 male children. The analysis of race-based
differences included data from 2202 white, 67 Asian, 222 Black, 131
Hispanic, and 93 ``Other'' children. Due to sparse data for many
categories, we binarized participants' race andethnicity as White (2202)
or Non-white (513), recognizing that there is important variation
between groups that this will fail to capture. Data for the maternal
education analysis included CDI data from children whose mothers had the
following levels of education: 8 with no more than primary school
education, 123 with some secondary school, 416 with no more than
secondary school, 613 with some college, 870 with no more than a college
degree, 162 with no more than some graduate school, and 584 with a
graduate degree. Again due to data sparsity, we binarized the 4973
children whose mothers had at least some college or more as high
maternal education (high-ME), and those whose mothers had at most high
school (547 children) as low maternal education (low-ME).

@@

First, we examine the size of demographic effects on language ability in
a baseline Rasch model fitted without regard to demographic group. Then
we fit a multigroup Rasch model for each demographic factor, and
characterize the between-group differences in item difficulties. Next,
we re-examine the size of demographic effects after pruning biased items
from the CDI:WS using different criteria, and recommend a threshold.
Finally, we measure the strength of association between sex-related
differences in language input and the degree of sex-related DIF.

\hypertarget{demographic-effects-in-the-baseline-rasch-model}{%
\subsection{Demographic effects in the baseline Rasch
model}\label{demographic-effects-in-the-baseline-rasch-model}}

@@

Figure 2 shows GLIMMERs for a selection of CDI items for sex (left),
maternal education (middle), and race (right). The full GLIMMERs, with
all 680 CDI:WS items, are available on
\href{https://osf.io/57rsw/?view_only=2b6ecb61fe08458293af7421d276932a}{OSF},
but were too large to include here. It is important, however, to inspect
the full plots, for if there is a cluster of items in a GLIMMER, the
analyst may conclude that these items are strong candidates for DIF on
that dimension. For example, there is some clustering at the top and
bottom of Figure 2: at the top, ``vagina''\footnote{Parents using the
  CDI are instructed to check genital items if the child produces
  whatever word the family uses.}, ``tights,'' ``dress (object),'' and
``doll'' form a cluster of items that are much more well-known for
females, while at the bottom, ``penis'' stands out as much more
well-known by males. For the maternal education and race GLIMMERs
(Figures 3 and 4) -- and in the rest of the full sex GLIMMER, there are
not clusters, but rather a continuum of smoothly varying differences
with overlap. This pattern makes identifying items with DIF quite
difficult, as different methods are likely to yield inconsistent results
(Stenhaug, Frank, \& Domingue, 2021). Hence, we next characterized the
distributions of the item-level group difficulty differences, and
measured the influence of pruning a varying number of items on the
demographic effect sizes.

@@

For sex, the median difficulty difference (male-female) was 0.28
(M=0.27, sd=0.4), with 593/680 items being easier for females than
males. The fact that the bulk of this distribution favors females shows
that the female language advantage is pervasive across the CDI:WS, and
suggests that it is likely to reflect more than the effect of a small
number of biased words (cf. Frank, Braginsky, Yurovsky, \& Marchman,
2021).

@@

For maternal education (ME), the median difficulty difference (low-high)
was -0.01 (M=0.03, sd=0.55), with 337/680 items being easier for high-ME
than low-ME children. With the mean and median difficulty differences
close to 0, and roughly half of the words favoring each ME group, it
seems that the CDI:WS items are somewhat balanced with respect to ME
(and thus SES, by proxy).

@@

If only a small number of items show DIF, pruning decisions are simple;
this situation was not the case for any of the three characteristics we
examined. Instead, distributions of DIF varied smoothly by each
demographic factor. Thus, we chose to evaluate multiple thresholds for
pruning the extreme-valued items from each distribution. For each
demographic factor, we pruned items with a between-group difficulty
difference from the mean difference at varying thresholds, from
\textgreater.25 SD to \textgreater3 SD, in increments of .25 SD. At each
SD threshold, a potentially different subset of items are excluded for
each model, but with the goal of creating a single CDI that is less
biased on all dimensions, we pruned the union of the subsets excluded
from each model. For example, pruning \textgreater2SD from the mean of
each model excluded 25 sex-biased items, 39 ME-biased items, and 31
race-biased items, with their union being 76 unique items. Figure 3
shows the demographic effects (\(\beta\)s) at different exclusion
thresholds.

@@

Where is the exclusion threshold that jointly minimizes the effect sizes
of these demographic variables? The strict exclusion of all items with
\textgreater.25 SD difficulty difference -- 661/680 (97\%) of the CDI:WS
-- best optimized this, but seems far too extreme of a culling. The next
best thresholds are \textgreater.5 SD -- again, too extreme -- or 3 SD,
a remarkably lax criterion that only excludes 19 items in total (11 due
to sex bias). Only slightly worse than these is \textgreater2.25 SD,
which excludes 59 items (9\%), and shows a modest effect of both race
(\(\beta=0.48\)) and maternal education (\(\beta=.19\)), and a
near-median effect size for sex (\(\beta=-.59\)). We characterize these
59 potentially biased items below, and consider whether we might
recommend pruning them from the CDI:WS.

@@

Demographic differences in language ability are likely to be at least
partially explained by differences in linguistic input received by
children in different groups. Indeed, input quantity (total daily
tokens) and some measures of quality (e.g., lexical diversity: ratio of
word types vs.~tokens) have often been predictive of language learning
outcomes in demographic studies (Huttenlocher, Haight, Bryk, Seltzer, \&
Lyons, 1991; Rowe \& Goldin-Meadow, 2009). We used a corpus-based
analysis to investigate the extent to which word frequency in
child-directed speech to male vs.~female children was predictive of the
amount of sex-based bias shown by CDI items. Similar to the approach
taken by Braginsky, Meylan, \& Frank (2016), we used the CHILDES corpus
of transcripts from dyadic play sessions (MacWhinney, 2000), which are
labeled with the sex of the target child, but not other demographic
variables. We found a total of 5213750 female-directed tokens and
6091950 male-directed tokens that matched 662 of the 680 CDI:WS items,
normalized the word frequencies to tokens per million for each target
sex, and calculated the log-odds of each word being spoken to a female
(i.e., \(log(p_{f} / p_{m}\)), meaning unbiased words will have log-odds
of 0, while those spoken more often to females will have log-odds
\(>0\), and those spoken more often males will have log-odds \(<0\). For
example ``doll'' was spoken 156 times to females, and 138 times to
males, thus \(p_{f} = 156/(156+138) = .53\), \(p_{m} = 1-p_{f} = 0.47\),
and \(log(p_{f}/p_{m})\) = 0.12), while ``police'' was spoken 138 times
to females, and 225 times to males, and thus has log-odds = -0.49).
Overall, the correlation between the log-odds of a word being spoken to
a female vs.~a male child and the size of the female (vs.~male)
advantage for that CDI word was modest, but significant (\(r=0.18\),
\(p<.001\)). Some of the sex bias seen in CDI items is related to
differences in language input received by girls vs.~boys -- though of
course this differential input could be elicited due to different
interests.

@@

We investigated the CDI:WS, a popular parent-report measure of
children's early vocabulary, for potential demographic bias, examining
the distribution of word difficulties for children of mothers with high
vs.~low education (a proxy for family SES), for female vs.~male
children, and for white vs.~non-white children. Our IRT-based analysis
revealed differential item functioning (DIF) for many items along each
demographic dimension, but only in the case of sex were clear clusters
of items that were more well-known to females (including feminine
clothing and genitalia), and a clear item that was more well-known to
males (male genitalia). For the rest of the items, and for SES- and
race-based analysis, there was a smooth continuum of DIF, making the
boundary of true DIF subjective. To move forward, we identified
candidate DIF items by systematically pruning the extremes of each
distribution, excluding outliers for each demographic across a range of
thresholds, and seeking to minimize the size of demographic effects.
Although many exclusion thresholds decreased the size of maternal
education and race effects, the female advantage actually grew under
most prunings, with the majority of excluded extrema being
stereotypically-male nouns (e.g, ``truck,'' ``fireman'').

This analysis highlights a fundamental difficulty of identifying DIF: an
analyst must either know the expected magnitude of an ability difference
between the two demographic groups, or know a set of ``anchor'' items
that are equally difficult (i.e., unbiased) for both groups (for an
overview, see Stenhaug, Frank, \& Domingue, 2021). But in the universe
of children's early language, there is only a finite set of
early-learned words to choose from -- and we may expect many of them to
be biased for various environmental reasons (e.g., boys and girls know
the names for their respective anatomy; children in Florida may not use
mittens or skis). Hence, the presence of DIF on a set of items could
indicate varying linguistic and environmental input, rather than an
actual advantage for one demographic over another.

Choosing an exclusion threshold that struck a balance of reducing race-
and ME-based bias and not eliminating too many items, we identified 59
items -- the majority of which favored white/high-ME groups. These
extrema were predominantly nouns, including many animals (esp.~for
maternal education), vehicles and professions (esp.~for sex). Notably,
no verbs and few syntactically complex items were identified as
outliers, which may suggest that these lexical classes are less prone to
bias via the internal or external mechanisms leading to the effects we
observed. Pruning these 59 outliers would slightly decrease the
demographic effects of maternal education (unpruned \(\beta=.23\);
pruned \(\beta=.19\)) and race (unpruned \(\beta=.50\); pruned
\(\beta=.48\)). In contrast, the majority of the sex-biased outliers
were easier for the disadvantaged group (males), meaning that the
removal of these extrema would increase the female language advantage on
the CDI:WS (unpruned \(\beta=0.56\); pruned \(\beta=.59\)). In
aggregate, these analyses seem to suggest that the CDI:WS may very
slightly overestimate the magnitude of differences in language ability
along the dimensions of maternal education and race, and perhaps
underestimate the female advantage.

This investigation is only a first step in measuring demographic bias in
the items on the CDI:WS. More research is needed to determine whether
CDI items that show DIF are more related to environmental frequencies,
as we found only a modest association between the relative frequency of
words in child-directed speech to boys vs.~girls and the amount of
sex-based DIF. Examining the relative frequency of CDI words across
households with varying maternal education and race may reveal similarly
weak associations, or there may be strong associations only among
particular categories of words. It may be that particular activity
contexts--popular with some demographic groups, and not others--may be
predictive. For example, many of the extrema favoring high-ME children
are animals and animal sounds (e.g., ``quack quack,'' ``woof woof,''
``baa baa,'' ``duck,'' ``sheep,'' ``giraffe,'' ``zebra''): do high-SES
households visit the zoo more often, or perhaps engage in other
activities related to naming animals and noises they make (e.g., animal
noise toys)? If certain activities are driving early word learning for
high-ME children, what are the activities (and associated vocabulary)
that low-SES households are instead engaging in? Critically this
enterprise will require a greater diversity of publicly-available
corpora of child language; we view the lack of such data as a
substantial issue.

SES, race, and sex are only three of many possible demographic
dimensions of interest. For example, geographic region is likely
predictive of children's early experience with (and thus knowledge of)
CDI items related to winter weather (e.g., ``snow,'' ``mittens'') or
outdoors activities (e.g.~``camping''). A truly fair test of children's
early vocabulary would contain a representative and balanced sample of
words from all activities that children engage in, across demographic
groups.
